The Impact of Education <br>

### 2014-12-04 Presentation/EdEntrePres.Rmd
Updated slides

## From Education to Entrepreneurship

@@

@@

@@

# Run a RE regression
Z1 <- zelig(PercentIntention ~ PercentPerceived + PercentFear*PercentOpportunities + WayofTeaching, data = CompleteData_omit, model = "ls")

>>>>

## Research Interest

@@

## Causal Chain

## Where our intuition came from

Variable | France | UK
-------------|---------------|---------
Fear of Failure (GEM 2012) | 43% | 36%
Perceived Capabilities (GEM 2012) | 36% | 47%
Sense of belonging (PISA 2012) | 47% | 79%

## What is PISA

- PISA: "Programme for International Student Assessment is a triennial international survey which aims to evaluate education systems worldwide by testing the skills and knowledge of 15 year old students."

- Data availability prevented us from using PISA data for this project

## What is GEM

- GEM: Global Entrepreneurship Monitor project is an annual assessment of the entrepreneurial activity, aspirations, and attitudes of individuals across a wide range of countries.

-

## Estimation Strategy

Variable | Indicator 
-------------|---------------
Y Dependent Vaiable | Rate of Entrepreneurship (Intention, Nascent, Established)
X1 Explanatory Variable | Way of Teaching
X2 Control Variable | Perceived Capabilities
X3 Control Variable | Fear of Failure / Perceived Opportunities
X4 Control Variable | Perceived Opportunities

## Explaining Way of Teaching

*How is it measured*

@@

## Perceived Capabilities

*What about it*

## Perceived Capabilities
```{r echo =FALSE, cache=TRUE, include=FALSE, results='asis'}

# Import GEM data frame
PerceivedCapabilities <- repmis::source_data("https://raw.githubusercontent.com/SamDund/Assign2Education/master/GEMData/GEM_PerceivedCapabilities.csv", header = TRUE, cache = FALSE, na.strings = "-")

## Add country codes and place new column at beginning of the data frame
# Create a vector of country codes
C2 <- countrycode(PerceivedCapabilities$Country, "country.name", "iso2c")

# Create a new column and insert the country code vector
PerceivedCapabilities$new.col <- C2

# Reorder columns so country code is first
C3 <- PerceivedCapabilities[,c(15,1:14)]

# Rename first column
C4 <- plyr::rename(x = C3, 
                   replace = c("new.col" = "iso2c"))

# Remove X's in D4 year columns
names(C4) <- gsub("X", "", names(C4))

# Set columns as numeric
C4[,"2001"] <- as.numeric(C4[,"2001"])
C4[,"2002"] <- as.numeric(C4[,"2002"])
C4[,"2003"] <- as.numeric(C4[,"2003"])
C4[,"2004"] <- as.numeric(C4[,"2004"])
C4[,"2005"] <- as.numeric(C4[,"2005"])
C4[,"2006"] <- as.numeric(C4[,"2006"])
C4[,"2007"] <- as.numeric(C4[,"2007"])
C4[,"2008"] <- as.numeric(C4[,"2008"])
C4[,"2009"] <- as.numeric(C4[,"2009"])
C4[,"2010"] <- as.numeric(C4[,"2010"])
C4[,"2011"] <- as.numeric(C4[,"2011"])
C4[,"2012"] <- as.numeric(C4[,"2012"])
C4[,"2013"] <- as.numeric(C4[,"2013"])

# Save cleaned df
Cap1 <- C4

# Generate a new column with mean of all other columns
C4$mean <- rowMeans(subset(C4, select = c("2001", "2002", "2003", "2004", "2005", "2006", "2007", "2008",
                                          "2009", "2010", "2011", "2012", "2013")), na.rm = TRUE)

# Drop year columns, leaving only mean column
C4$'2001' <- NULL
C4$'2002' <- NULL
C4$'2003' <- NULL
C4$'2004' <- NULL
C4$'2005' <- NULL
C4$'2006' <- NULL
C4$'2007' <- NULL
C4$'2008' <- NULL
C4$'2009' <- NULL
C4$'2010' <- NULL
C4$'2011' <- NULL
C4$'2012' <- NULL
C4$'2013' <- NULL

# Create 
C4[, 3] <- round(log(C4[, 3]), digits = 2)
```

# Plot perceived opportunties map
Cap1_map <- gvisGeoChart(C4, locationvar = 'iso2c',
                      colorvar = 'mean',
                      options = list(
                        colors = "['#ece7f2', '#2b8cbe']"
))

# Duplicate D4 (perceived capabilities) df
Cap4 <- C4

# Drop iso2c in Dropped4
C4$iso2c <- NULL

# Print the table
print(Cap1_map, tag = 'chart')

# Subset Cap4
Cap5 <- subset(Cap4, iso2c %in% myvars2)

# Melt Opp2 df
Cap6 <- melt(data = Cap5,
                  id.vars = c("Country", "iso2c"),
                  measure.vars = c("2001", "2002", "2003", "2004", "2005", "2006",
                                   "2007", "2008", "2009", "2010"))

# Edit column names
names(Cap6) <- gsub("value", "Capabilities", names(Cap6))
names(Cap6) <- gsub("variable", "Year", names(Cap6))

Cap6$iso2c <- NULL
```

# Create plot
ggplot(Cap6,aes(x = Year, y = PerceivedCapabilities, colour = Country, group = Country)) + geom_line()

@@

# Run a RE regression
Z1 <- zelig(PercentIntention ~ WayofTeaching + PercentPerceived + PercentFear*PercentOpportunities + PercentOpportunities, data = CompleteData_omit, model = "ls")
